Output Summary

### 2021-10-22 03-post-process/output-plots.Rmd
Move creation of vcov_labels/indices

ko_origin = list(
  ko_nor = 1:3,
  ko_hor = 4:6
)
```

>>>>

ko_origin = list(
  ko_nor = 1:3,
  ko_hor = 4:6
)

# make the labels for which elements of the rho matrices contain unique elements
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
```
